### 2014-03-12 src/methodology.Rnw
update

>>>>

For the first variant, we applied the x\% sampling to the result of the first
sampling based on line counts. That is, in the case of methods, we first
selected \textit{linecount} mutants each from each method, and applied the x\%
selection to the result of this selection. For the second variant, we did
the sampling in one go, where we chose \textit{linecount/x} number of mutants from
each program element.

### 2014-03-12 src/results.Rnw
update

The Table~\ref{tbl:lcountl} provides the results for line count criteria.

>>>>

The Table~\ref{tbl:lcountl} provides the results for line count criteria where the
sampling was conducted outside program element, and Table~\ref{tbl:lcountw} contains
the results for line count criteria where the sampling was conducted inside the
program element.
